\textbf{Computational Fuzzy Extractors}

### 2013-03-19 CompFuzzExt.tex
Cleanup up full rank notation in Theorem 5.3

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

@@

The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$.  Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
\bnote{We should add some exposition here.  Some intuition about the proof.}

@@

\bnote{Need to continue and go through their Lemma 2.1 and 2.4 to be sure I believe this.  Everything else should go through fine.}

@@

\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
We have the following for all $i=1,..., m+\alpha$:
\begin{align*}
\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
\end{align*}
%\begin{align*}
%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
%& = b_i \label{reductionEq}
%\end{align*}
\end{proof}
\begin{claim} 
\label{clm:random b}
If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
\end{claim}
\begin{proof}
Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
\[
b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
\]
%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each

$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{I need show more work on this, maybe?}
Thus, each of these values is uniformly and independently random.
\end{proof}

%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$. 
%
%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$. Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
%\begin{align*}
%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
%\end{align*}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
\end{align*}
%==========
\ignore{
Before randomized:
$$\vA'\vx' + \ve = \vb'$$
For $i = 1\ldots m$,
$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
For $i = 1\ldots \alpha$,
$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
}
\end{proof}

\section{Additional Proofs}

>>>>

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

@@

The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
\bnote{We should add some exposition here.  Some intuition about the proof.}

@@

\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}

@@

\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
We have the following for all $i=1,..., m+\alpha$:
\begin{align*}
\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
\end{align*}
%\begin{align*}
%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
%& = b_i \label{reductionEq}
%\end{align*}
\end{proof}
\begin{claim} 
\label{clm:random b}
If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
\end{claim}
\begin{proof}
Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
\[
b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
\]
%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each

$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
Thus, each of these values is uniformly and independently random.
\end{proof}

%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$. 
%
%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$. Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
%\begin{align*}
%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
%\end{align*}

\begin{claim}
If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
\end{claim}
\begin{proof}
Assume that $(\vA', \vb')$ is uniformly distributed.  By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.  Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.  Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.  
We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.  Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.  Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$. Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.  Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.  Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.

 \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.  If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.  It does with very high probability, but I don't want to add this restriction.  Is there a way to get around this problem?}
%\[
%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) 
%\]
%\begin{align*}
%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
%\end{align*}
\end{proof}
\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
\end{align*}
%==========
\ignore{
Before randomized:
$$\vA'\vx' + \ve = \vb'$$
For $i = 1\ldots m$,
$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
For $i = 1\ldots \alpha$,
$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
}
\end{proof}

\section{Proof of Theorem \ref{thm:blockLWE} Revised}
\label{sec:proof of block theorem}

%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.  If the blocks are fixed to some other value the reduction is essentially the same.  For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.  Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.  We use similar notation for the complement of $T$, denoted $T^c$.

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.  That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.  We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Let $\epsilon \geq 1/\poly(n)$, then, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  It suffices to build a distinguisher $\D'$ whose size at most \bnote{fill in} bigger than $\D$ where 
\begin{align}
\label{eq:block LWE dist}
|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., n$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., n$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$, thus by union bound this probability is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

We restrict analysis to the case where $\rank(\vS) = \alpha$.  
It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
\end{enumerate}

\begin{claim}
\label{cl:randomMatrixDist}
The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix with $\rank(\vS) = \alpha$.
\end{claim}
\begin{proof}
It should be clear that $\vR, \vS$ are randomly generated~(conditioned on $\rank(\vS) =\alpha$).  The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.  
The matrix $\vW_{T^c}$~(recall this is the restriction of $\vW$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.

Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).  Fix a particular row $i$.  Then $\vW_{i, T} = \gamma_i \vS_{T}$.  Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vW_{i, T}$ is uniformly generated.

Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(\vS) = \alpha$.
% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
\begin{claim}
\label{cl:random ax+e}
If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.  We define the remaining variables $\vx_T$ as the solution to the following system of equations.
\vS_T  \vx_T = \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
A solution $\vx_T$ exists as $\vS_T$ is full rank and $\vx_T$ is uniformly distributed.
Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.  The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$.  Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.  The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
We have the following for $1\leq i\leq m$:
\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
\\&=  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
This completes the proof of the claim.
\begin{claim}
If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
\bnote{This needs to be checked.}
Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.  The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$.  That is, for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.  Thus $b^* | \vA^*$ is uniformly distributed.  Instead of showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}, we show that $\vb |( \vA, \vA^*)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.  Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.  Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$. Recall that 
 \[
 \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
\]
Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
\end{proof}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
&\left|\Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right] \Pr[\rank(\vS) = \alpha] \right|\\
&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
\end{align*}
Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
\end{proof}
\section{Additional Proofs}
